Automated Timed Temporal Verification

### 2022-07-07 paper/popl2022.tex
m

\begin{figure}[h]
\noindent
   \vspace{-2mm}
\begin{varwidth}{.5\textwidth}
\begin{lstlisting}
function enableLoginButton(){
  return (Rname.length >= 2 
	   && Rpasswd.length >= 2);}
function nameKeypress(value){
  Rname = value;
  RenableLogin=enableLoginButton();}
function passwdKeypress(value){ 
  Rpasswd = value;
  RenableLogin=enableLoginButton();}
\end{lstlisting}
\end{varwidth}%
\begin{varwidth}{.5\textwidth}
\begin{lstlisting}
hiphop module Identity(
			in name, in passwd, 
			out enableLogin){
  do{
	  emit enableLogin(
		  		name.length >= 2 
		  	 && passwd.length >= 2); 
  } every(name || passwd)
}
\end{lstlisting}  
\end{varwidth}
      \vspace{0mm}
\caption{A comparison between JavaScript (left) and HipHop.js (right) for a same login button implementation \cite{berry2020hiphop}. (On the right, {\ttfamily{name}}, {\ttfamily{passwd}} and {\ttfamily{enableLogin}} are reactive input/output signals.)}
  \label{fig:login_compare}  
      \vspace{0mm}
\end{figure}

@@

\begin{wrapfigure}{R}{0.5\columnwidth}
      \vspace{-2mm}
\begin{lstlisting}[columns=fullflexible]
hiphop module send (var n, out Send, out Done)
/*@ requires true : ε @*/
/*@ ensures	(n>=0 : {}^*. {Done}) 
          ∨ (n<0   : {Send}^w)  @*/
{
	if (n==0) { emit Done; }
	else {
		emit Send;
		yield;
		send (d, n-1, Send, Done); }}
\end{lstlisting}  
      \vspace{-1mm}
      \caption{A recursive \ttfamily{Send} module.}\label{fig:case_study_finit_infinit}
         \vspace{-2mm}
\end{wrapfigure}

>>>>

\begin{figure}[h]
\noindent
   \vspace{-2mm}
\begin{varwidth}{.5\textwidth}
\begin{lstlisting}
function enableLoginButton(){
  return (Rname.length ≥ 2 
	   && Rpasswd.length ≥ 2);}
function nameKeypress(value){
  Rname = value;
  RenableLogin=enableLoginButton();}
function passwdKeypress(value){ 
  Rpasswd = value;
  RenableLogin=enableLoginButton();}
\end{lstlisting}
\end{varwidth}%
\begin{varwidth}{.5\textwidth}
\begin{lstlisting}
hiphop module Identity(
			in name, in passwd, 
			out enableLogin){
  do{
	  emit enableLogin(
		  		name.length ≥ 2 
		  	 && passwd.length ≥ 2); 
  } every(name || passwd)
}
\end{lstlisting}  
\end{varwidth}
      \vspace{0mm}
\caption{A comparison between JavaScript (left) and HipHop.js (right) for a same login button implementation \cite{berry2020hiphop}. (On the right, {\ttfamily{name}}, {\ttfamily{passwd}} and {\ttfamily{enableLogin}} are reactive input/output signals.)}
  \label{fig:login_compare}  
      \vspace{0mm}
\end{figure}

@@

\begin{wrapfigure}{R}{0.5\columnwidth}
      \vspace{-2mm}
\begin{lstlisting}[columns=fullflexible]
hiphop module send (var n, out Send, out Done)
/*@ requires true : ε @*/
/*@ ensures	(n≥0 : {}^*. {Done}) 
          ∨ (n<0   : {Send}^w)  @*/
{
	if (n==0) { emit Done; }
	else {
		emit Send;
		yield;
		send (d, n-1, Send, Done); }}
\end{lstlisting}  
      \vspace{-1mm}
      \caption{A recursive \ttfamily{Send} module.}\label{fig:case_study_finit_infinit}
         \vspace{-2mm}
\end{wrapfigure}
